---
title: "Pricing Model for Residential Properties in King County, Washington"  
subtitle: "HARVARD EXTENSION SCHOOL"
author:
- John Hur
- Kacper Lewtak
- German Parades
- Lauren Briese
- Michael Lefkoe
- Rajesh Jain

tags: [linear reression, polynomial regression, regression tree]

abstract: |
  This group homework is part of Harvard Extesion course CSCI E-106 Section 1 (Data Modelling) class. This study examines the data of homes sold between May 2014 and May 2015 in King County, USA and proposes a Polynomial Regression Model to enable future predictions and decision making in the real estate market.

date: "`r format(Sys.time(), '%d %B %Y')`"
geometry: margin=1.3cm
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    df_print: paged
editor_options: 
  markdown: 
    wrap: sentence
---
\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings = FALSE,
                      message = FALSE, fig.align='center')

options(scipen = 999)

library(tidyverse)
library(kableExtra)
library(lmtest)
library(MASS)
library(onewaytests)
library(olsrr)
library(car)
library(broom)
library(readr)
library(datasets)
library(faraway)
library(fastDummies)
library(tibble)
library(corrplot)
```
\newpage
## House Sales in King County, USA data to be used in the Final Project

| Variable| Description |
| :-------:| :------- |
| id| **Unique ID for each home sold (it is not a predictor)**    |
| date| *Date of the home sale*    |
| price| *Price of each home sold*    |
| bedrooms| *Number of bedrooms*    |
| bathrooms| *Number of bathrooms, where ".5" accounts for a bathroom with a toilet but no shower*    |
| sqft_living| *Square footage of the apartment interior living space*    |
| sqft_lot| *Square footage of the land space*    |
| floors| *Number of floors*    |
| waterfront| *A dummy variable for whether the apartment was overlooking the waterfront or not*    |
| view| *An index from 0 to 4 of how good the view of the property was*    |
| condition| *An index from 1 to 5 on the condition of the apartment,*    |
| grade| *An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of construction and design, and 11-13 has a high-quality level of construction and design.*    |
| sqft_above| *The square footage of the interior housing space that is above ground level*    | 
| sqft_basement| *The square footage of the interior housing space that is below ground level*    |
| yr_built| *The year the house was initially built*    |
| yr_renovated| *The year of the house’s last renovation*    |
| zipcode| *What zipcode area the house is in*    |
| lat| *Latitude*    |
| long| *Longitude*    |
| sqft_living15| *The square footage of interior housing living space for the nearest 15 neighbors*    |
| sqft_lot15| *The square footage of the land lots of the nearest 15 neighbors*    |
\newpage

## Executive Summary

A study was conducted on the house sale prices between May 2014 to May 2015 in King County, USA. The purpose of the study was to build a predictive model to enable decision making and to reduce risk during our automated underwriting process that relies on automated valuation of properties. Through this study, we analyzed data on more than 21,000 houses sold during the year, and across 17 variables that included, among others, the number of bedrooms, the number of bathrooms, the square footage of the house, zip code. We propose a Polynomial Regression Model in this study.

The model is intended to be used as a tool to help make decisions and to reduce risk and enable faster pre-approvals, and is not intended to be used as a replacement for a professional appraisal as it has several limitations including inconsistencies in data that need further investigation. The model is also based on a limited geographical area and may not be applicable to other areas outside of King County, USA. Because the model is based on a limited time frame, it should be continually monitored and updated with the latest pricing.

\newpage
## I. Introduction (5 points)

### I.I Problem Statement

Our current pre-approval process relies on property value based on just 6 buckets corresponding to the conforming, jumbo and subprime loan limits based on Zip Code. This leads to sub-optimal decision making that increases the risk of default, and at the same time, leads to lost opportunities for the bank by denying a pre-approval to a person who is otherwise highly credit worthy. 


### I.II Purpose and Scope

The goal of this study is to build a model that can be used to predict the value of a property more accurately based on the characteristics of the property. The scope of this study is limited to the King County, USA area and is based on the actual sales price of over 21,613 houses sold between May 2014 and May 2015 and is based on 17 characteristics of a typical home.

### I.III Methods

The predictive model was developed using Statistical Analysis using multiple regression models. We employed rigorous exploratory analysis of data, built multiple models including Linear, Polynomial, Weighted Least Square and Regression Tree models, and used a variety of statistical tests to ensure that the model is robust and reliable.

We started with extensive exploratory analysis to understand the data and to identify any missing values, outliers and inconsistencies. Through this analysis, we excluded variables that were either not relevant to the model as they were not a characteristic of a property, or were highly correlated to avoid overfitting. Next we split the data and utilized 70% of the observations to train a model, and the rest 30% to test the performance of the models. 

We built multiple candidate Linear models, and utilized statistical techniques, to identify and retain the characteristics of the property which were most significant in explaining the price of a house. We also conducted a variety of both visual and statistical tests to ensure that the model is compliant with the assumptions of Normality, Linearity, Homoscedasticity and Independence.This helped narrow down to a "champion" model, which formed our baseline for further analysis.

Next, we built some non-linear "challenger" models, including Polynomial, Weighted Least Square and Regression Tree to compare the robustness, reliability and performance of the models, the most promising of which were a Polynomial model and the Regression Tree model. We again conducted numerical statistical tests by using the 30% test data to understand a models predictive power. We concluded by picking a Polynomial model, but also suggesting Regression Tree could be an alternate because the performance of the models was relatively close. 

### I.IV Limitations

Lastly, we ensured we documented the limitations and risks of such a model given that it was based on a limited geographical area and a limited time frame. We also identified some inconsistencies in the data that need further investigation and could result in incorrect predictions.

\newpage
## II. Description of the data and quality (15 points)

### II.I Data Load and Inspection

```{r import house sales data}
# read in data
kc_house_sales = read.csv('KC_House_Sales.csv')

# get number of N/A values in each column
colSums(is.na(kc_house_sales))

# get column names, data types, and first few values for each column
str(kc_house_sales)
```

The data to be analyzed in this report is a set of housing sales data from King County, USA in the 2014-2015 time frame. King County is the most populous county of Washington, and the county seat is Seattle [1]. The original data set contains 21 columns with 21613 observations. There are no N/A values in the data set that need to be removed or addressed. Although there are some questionable values in the data set (for example, a house with 33 bedrooms, houses with 0 bathrooms and 0 bedrooms), there are few enough and without additional context or the ability to get clarification on these possible outliers, we did not drop any observations before developing the models.

### II.II Data Cleanup

We took the following steps to prepare data prior to developing the models.

```{r convert price to numeric}
# convert the price to a numeric column
kc_house_sales$price = as.numeric(gsub('\\$|,','',kc_house_sales$price))
```
  
We updated the price column to numeric as it is the response variable which we built the models to predict.

```{r convert }
# create n_yrs_ago_built
kc_house_sales$date = as.numeric(substr(kc_house_sales$date, start = 1, stop = 4))
kc_house_sales$n_yrs_ago_built = max(kc_house_sales$date) - kc_house_sales$yr_built
```

We used the difference of the maximum year from the sales date and the year built to create a new variable **n_yrs_ago_built** to determine how many years ago the house was built.

```{r convert zip code to character data types}
# convert zip code to characters so it will create dummy variables
kc_house_sales$zipcode = as.character(kc_house_sales$zipcode)

# convert waterfront to categorical
kc_house_sales$waterfront = as.factor(kc_house_sales$waterfront)
```

We converted zip code to a character column and treated it as a categorical variable. Although it appears numeric, zip codes are used as identifiers. In addition, waterfront is categorical per the description from the original data set, and was converted to a factor. The date field is categorical, but we chose to drop it.

```{r drop id, lat, long, yr_renovated, sqft_basement, date}
kc_house_sales = subset(kc_house_sales, select = -c(id, lat, long, yr_built, 
                                                    yr_renovated, sqft_basement, date))
```

We dropped the following columns prior to beginning model development:  
- id: This is not a predictor or relevant to the sales data beyond being an identifier for each row.  
- lat: This level of detail is not necessary, and the zipcode column also approximates location.  
- long: This level of detail is not necessary, and the zipcode column also approximates location.
- date: This was removed since all house sales were within the same 13-month period.
- yr_built: Removed in favor of the calculated n_yrs_ago_built.
- yr_renovated: Removed in favor of the calculated n_yrs_ago_built.
- sqft_basement: This column is equal to sqft_living - sqft_above, so it does not provide new information and its inclusion would lead to multicollinearity.

### II.III Correlation for Numeric Variables

```{r data correlation for numeric variables, fig.width=9, fig.height=9}
# get correlation of numeric data, rounded for ease of review)
kc_house_sales_numeric = subset(kc_house_sales, select = -c(waterfront, zipcode))

#correlation plot
cor_matrix <- round(cor(kc_house_sales_numeric),3)
corrplot(cor_matrix, method = "number", title = "Correlation Matrix", 
         tl.col = 'black', mar=c(0,0,1,0), number.digits = 3, number.cex=0.9)
```
  
Looking at the correlation matrix above for the numeric columns in the data set, price appears to be most correlated with the fields sqft_living (0.702), grade (0.667), and sqft_above (0.606). **Note that the categorical variables waterfront and zipcode are not included in the correlation matrix.**

The sqft_living and sqft_above variables have a high correlation; it may be worth including only one of these in the model. For houses without basements, the sqft_living and sqft_above values should be equal.

### II.IV Exploratory Analysis
The following sections describe the response variable (price) and the predictor variables that we ultimately included in our models. Appendix C contains additional plots and discussion of predictor variables that were not included in the final models.

#### II.IV.I Price
```{r price scatter plots, box plots, histograms}
# price box plot and histogram
par(mfrow=c(1,2))
boxplot(kc_house_sales$price, main = "Figure 2-1. Price Box Plot")
hist(kc_house_sales$price, main = "Figure 2-2. Price Distribution", xlab="Price ($)")
mean(kc_house_sales$price)
median(kc_house_sales$price)
```
  
We updated the price column to a numeric column since it could not be analyzed with the character type. The median sales price for the observations was \$450,000, and the average was \$540,088.10. Per Figure 2-1, it appears as though there are many outliers in the data on the higher end of the price range. Figure 2-2 confirms this assumption, showing that the distribution of sales prices has a much higher frequency at the lower end of the range.

#### II.IV.II Square Footage - Living
```{r housing square footage living scatter plots, box plots, histograms}
# sqft_living box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$sqft_living, main = "Figure 2-3. Sqft_living Box Plot", xlab="Sqft_living")
hist(kc_house_sales$sqft_living, main = "Figure 2-4. Distribution of Sqft_living", xlab = "Sqft_living")
par(mfrow=c(1,1))
plot(kc_house_sales$sqft_living, kc_house_sales$price,  main = "Figure 2-5. Sqft_living Scatter Plot",
     xlab="Sqft_living", ylab="Price ($)");
abline(lm(kc_house_sales$price ~ kc_house_sales$sqft_living), col = "red")
```
  
Per Figure 2-3 and 2-4, the median square footage of living space appears to be around 2000 sqft, with outliers present at the higher end of the range.

Per Figure 2-5, there appears to be a linear relationship between square feet of living space and price, with price increasing as the square footage increases.

#### II.IV.III View
```{r view scatter plots, box plots, histograms}
# view box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$view, main = "Figure 2-5. View Box Plot")
hist(kc_house_sales$view, main = "Figure 2-6. View Distribution", xlab = "View")
par(mfrow=c(1,1))
plot(kc_house_sales$view, kc_house_sales$price,  main = "Figure 2-7. View Scatter Plot",
     xlab = "View", ylab = "Price ($)")
```
  
Looking at Figure 2-5 and Figure 2-6, most houses do not have a view; according to the box plot, any house with a view appears to be an outlier. Per Figure 2-7, the price does not seem to increase or decrease much depending on the house's view.

#### II.IV.IV Grade
```{r grade scatter plots, box plots, histograms}
# grade box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$grade, main = "Figure 2-8. Grade Box Plot")
hist(kc_house_sales$grade, main = "Figure 2-9. Grade Distribution", xlab = "Grade")
par(mfrow=c(1,1))
plot(kc_house_sales$grade, kc_house_sales$price,  main = "Figure 2-10. Grade Scatter Plot",
     xlab = "Grade", ylab = "Price ($)");
abline(lm(kc_house_sales$price ~ kc_house_sales$grade), col = "red")
```

According to the box plot and histogram in Figure 2-8 and 2-9, the median grade appears to be 7, which is an "average" quality, and outliers are any grade outside the range of 6 to 9. The scatter plot in Figure 2-10 indicates that grade appears to have a linear relationship with prices, with the price increasing as the grade of the house increases.

#### II.IV.V Years Ago Built
```{r years ago built scatter plots, box plots, histograms}
# grade box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$n_yrs_ago_built, main = "Figure 2-11. N_yrs_ago_built Box Plot")
hist(kc_house_sales$n_yrs_ago_built, main = "Figure 2-12. N_yrs_ago_built Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$n_yrs_ago_built, kc_house_sales$price,  
     main = "Figure 2-13. N_yrs_ago_built Scatter Plot");
abline(lm(kc_house_sales$price ~ kc_house_sales$n_yrs_ago_built), col="red")
```

As discussed above, we create a new variable, n_yrs_ago_built by subtracting the year the house was built from 2015, the maximum  sales date from the data set. The box plot in Figure 2-11 shows that the median age of houses sold was 40 years, with no outliers in the data set. The distribution of houses sold appears to skew towards newer houses per Figure 2-12. Looking at the scatter plot, the number of years ago built does not appear to have a strong relationship to the price of the house.  It would be interesting to look at this variable in combination with other factors, such as zip code (e.g. was one desirable neighborhood/zip code built at a certain time and does that affect the price?).

#### II.IV.VI Waterfront

```{r waterfront box plot}
boxplot(kc_house_sales$price ~ kc_house_sales$waterfront , main = "Figure 2-14 Waterfront Box Plot"
        , col = c("red", "blue"), pch=19, cex=0.5)
```
Waterfront is a categorical variable, with houses either on the waterfront (1) or not (0). From the box plot in Figure 2-14, it appears as though having a waterfront view may lead to higher prices; the median price of houses with a waterfront view is much higher.

#### II.IV.VII Zip Code

```{r zip code box plot, include=FALSE}
boxplot(kc_house_sales$price ~ kc_house_sales$zipcode , 
        main = "Figure 2-15 Zipcode Box Plot", pch=19, cex=0.5)
```

As discussed above, we chose to use zip code as a categorical variable since it is used as an identifier rather than a number whose value has any meaning. There are 70 unique zip codes in the data set. The box plot in Figure 2-15 shows a wide range in the median value of house prices in certain zip codes, with several outliers for most of the zip codes. At first glance, it seems as though the oft-repeated "location, location, location" phrase may be true for this data set.

\newpage
## III. Model Development Process (15 points)

```{r data_import}
# Import house price data
kc_house_sales <- read_csv('KC_House_Sales.csv') %>%
  mutate(price = as.numeric(str_remove_all(price, '[$,]'))) %>% 
  dplyr::select(-id, -lat, -long)

yr_max <- year(max(kc_house_sales$date))

# Transform variables where needed (NOTE: be sure to discuss in data quality 
# section why we dropped sq ft of basement and year renovated)

kc_house_sales_transf <- kc_house_sales %>% 
  mutate(n_yrs_ago_built = yr_max - yr_built,
         zipcode = as.character(zipcode)) %>% 
  dplyr::select(-date, -yr_built, -yr_renovated, -sqft_basement)

```


```{r train_test_split}
# Split into train (70%) and test sets
set.seed(1023)
n <- nrow(kc_house_sales_transf)
train_i <- sample(n, size = 0.7*n)

train_df <- kc_house_sales_transf[train_i,]
test_df <- kc_house_sales_transf[-train_i,]
```


### III.I Estimation of Full Model

Prior to conducting any variable selection or variable transformations, we estimate the linear regression model using all predictors. Note that the zipcode variable is a categorical variable with 70 unique zipcodes. In our model, we consider this to be one variable with 70 degrees of freedom, i.e., there will be a separate dummy variable for 69 of the 70 zipcodes. 

The results from the full model estimation are shown below. Every variable is significant at the 95% level of significance, except for square feet of living space for the nearest 15 neighbors. Furthermore, the adjusted R-squared is .803, meaning that the predictors explain about 80.3% of the variation in the response variable. 

The fact that almost every variable is significant suggests that if we were to do backward or forward stepwise selection process based on p-values alone, we would most likely end up with nearly all of the variables still in the model. Thus, it makes more sense to consider a performance metric like AIC or adjusted R-squared and include only the variables that provide material lift to those metrics, rather than all significant variables. 

```{r full_model}
# Estimate the full model using training data (zipcode dummy vars created automatically)
full_model <- lm(price ~ ., data = train_df)

# Display results
tidy(full_model) %>% 
  dplyr::select(Term = term, Coefficient = estimate, std.error, p.value) %>% 
  mutate(Coefficient = round(Coefficient, 3),
         std.error = round(std.error, 4),
         p.value = round(p.value, 4)) %>% 
  filter(!str_detect(Term, 'zipcode')) %>% 
  kable(caption = "Full OLS Model - All Predictors (zip code not shown, but predictor is included in model)",
        booktabs = T,) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")

```

### III.II Forward Stepwise Selection (AIC)

Using the AIC as the selection criteria for forward stepwise selection, we can find that most variables drive a reduction in the AIC and adjusted R-squared, as shown in the table below. However, only a small handful of variables provide a material amount of additional lift, as the others barely move the needle on AIC and adjusted R-squared. 

The two variables that absolutely must be in the model are sq ft of living space and zip code, as the model with just those two variables gets us most of the way there to the levels of AIC and adjusted R-squared seen when all variables are included. This makes sense from an intuitive standpoint, as location is well-known to be one of the most important things people consider when buying a home and rich people typically live in large homes. 

We can also consider including waterfront, view, grade, and age of the home, as they provide a mild amount of additional lift. But after these variables, the remaining variables, despite being significant, provide minimal impact to the adjusted R-squared or AIC. 

```{r for_step_aic}
# Use AIC forward stepwise selection
ols_step_forward_aic(full_model)

```

### III.III Best Subsets Variable Selection 

This part will only consider sqft_living, zipcode, waterfront, view, grade, and age as potential variables, following the discussion in the previous section. To identify the best combination of these six variables to include in the final model, we consider all possible subsets of the variables, of which there are 63 total subsets. In the table below, we present the best subset for each value of p, where p is the number of variables in the model. 

To identify the best model, we can use the "elbow method", which is a useful rule of thumb that suggests choosing the value for p for which subsequent values provide minimal additional lift. Using the elbow method, it appears that "model 2", which includes only sqft_living and zipcode, is the best model. This is our first candidate for the final regression model. 

The second candidate model is the one that includes all six variables considered in this section. The intuition behind doing so is because not only do the additional four variables provide an additional 6.8% boost to the R-squared, but the second candidate is also more intuitive and easier to explain to stakeholders, who may find it undesirable to include just two variables in a house pricing model. 

To summarize, the two final candidate models for the linear regression model are as follows:
 
**Candidate 1: Price = sqft_living + zipcode **

**Candidate 2: Price = sqft_living + zipcode + waterfront + view + grade + n_yrs_ago_built **


```{r reduced_models, fig.show='hold', out.width='50%'}
# Construct the reduced model
reduced_model <- lm(price ~ sqft_living + waterfront + view + grade + n_yrs_ago_built + 
                      zipcode, data = train_df)

reduced_forward <- ols_step_best_subset(reduced_model)

reduced_forward

plot(reduced_forward)
```

\newpage
## IV. Model Performance Testing (15 points)


*Use the test data set to assess the model performances. Here, build the best multiple linear models by using the stepwise both ways selection method. Compare the performance of the best two linear models. Make sure that model assumption(s) are checked for the final linear model. Apply remedy measures (transformation, etc.) that helps satisfy the assumptions. In particular you must deeply investigate unequal variances and multicollinearity. If necessary, apply remedial methods (WLS, Ridge, Elastic Net, Lasso, etc.). *

In this section, we examine the performance of the two best models found in the section above along multiple dimensions. First, we check the assumptions of the linear regression model and apply remediation measures as needed, such as the addition of polynomial terms, weighted least squares, robust regression, and variable transformation.

### IV.I Performance of Candidate OLS Models

Two OLS models were identified as candidate models in the previous section, referred to as Candidate 1 and Candidate 2. To determine which of the two models to examine and refine further, we must compare the performance of the two models on the test set using two metrics: adjusted R-squared and root mean squared error (RMSE). The results are shown below. 

Clearly, Candidate 2 is the better model, as it performs much better than candidate 1 on the test set with regards to both the adjusted R-squared and RMSE. Thus, for the remainder of this section, we choose to refine the second candidate model, which has the following six variables: 

- Square feet of living space
- Zip Code
- Waterfront 
- Grade
- View
- Age of Home

```{r best_ols_models, results='asis'}
# Estimate best models
best_ols_cand1 <- lm(price ~ sqft_living + zipcode, data = train_df)
best_ols_cand2 <- lm(price ~ sqft_living + waterfront + view + grade + 
                       n_yrs_ago_built + zipcode, data = train_df)

# Calculate RMSE for each model

# Get predictions on test set
cand1_yhat <- predict(best_ols_cand1, newdata = test_df)
cand2_yhat <- predict(best_ols_cand2, newdata = test_df)

# Get observed values for response
y_actual <- test_df %>% pull(price)

# Calculate RMSE
rmse_ols1 <- sqrt(sum((y_actual - cand1_yhat)^2) / nrow(test_df))
rmse_ols2 <- sqrt(sum((y_actual - cand2_yhat)^2) / nrow(test_df))

# Function to calculate adjusted R-squared
calc_rsq_adj <- function(n, p, sse, sst) {
  r_sq <- 1 - sse / sst
  adj_r_sq <- 1 - (1 - r_sq) * (n - 1) / (n - p - 1)
  return(adj_r_sq)
}

# SST and SSE
sst_test <- sum((y_actual - mean(y_actual))^2)
sse_cand1_test <- sum((y_actual - cand1_yhat)^2)
sse_cand2_test <- sum((y_actual - cand2_yhat)^2)

# Calculate adjusted R-squared for each model
n <- nrow(test_df)
adj_rsq_cand1 <- calc_rsq_adj(n, best_ols_cand1$rank - 1, sse_cand1_test, sst_test)
adj_rsq_cand2 <- calc_rsq_adj(n, best_ols_cand2$rank - 1, sse_cand2_test, sst_test)

# Put results into a table
results_df <- tibble(Model = c('OLS Candidate 1', 'OLS Candidate 2'), 
                         RMSE = c(rmse_ols1, rmse_ols2),
                         `Adjusted R-squared` = c(adj_rsq_cand1, adj_rsq_cand2))

kable(results_df, 
      format.args = list(big.mark = ","),
      booktabs = T,
      caption = ' Root Mean Squared Error (RMSE) and Adjusted R-squared on the Test Set for the Two Candidate Linear Regression Models') %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")


```

### IV.II Estimation of Candidate Model 2

The results from the estimation of candidate model number 2 are shown below. Signs on each of the coefficients follow intuition, as a unit increase in each of the variables (except for zip code) are intuitively expected to increase price. This is consistent with positive signs on each of those variables. 

```{r model2_estimation}
# Show summary of candidate 2
tidy(best_ols_cand2) %>% 
  dplyr::select(Term = term, Coefficient = estimate, std.error, p.value) %>% 
  mutate(Coefficient = round(Coefficient, 3),
         std.error = round(std.error, 4),
         p.value = round(p.value, 4)) %>% 
  filter(!str_detect(Term, 'zipcode')) %>% 
  kable(caption = "Candidate OLS Model 2 (zip code not shown, but predictor is included in model)",
        booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")

```

### IV.III Model Diagnostics

In this section, the model assumptions to check are: Linearity, Homoskedasticity, Error Normality, and no multicollinearity. From here on, the term "model" refers to candidate 2 above. 

#### IV.III.I Linearity Assumption

We can test the linearity assumption by plotting the residuals against the fitted values. From the plot below, it seems that the linearity assumption is valid on most of the data, except for the most expensive homes, where the model consistently underestimates price. This suggests that a polynomial term may be useful to help better predict the more expensive properties. 

```{r linearity_test}
# Plot residuals against fitted values
plot(best_ols_cand2, which = 1)

```

#### IV.III.II Homoskedasticity Assumption

To test the equal variances assumption, we can examine a scale-location plot. From the plot below, it's very clear that this assumption is violated. We can confirm this with the Breusch-Pagan test, which has a null hypothesis of equal variances and an alternative hypothesis of unequal variances. The result of this test is also shown below. As the p-value is nearly zero, we can very confidently reject the null of equal variances. 

```{r homosk_plot}
# Plot scale-location
plot(best_ols_cand2, which = 3)

# Breusch-Pagan test
bptest(best_ols_cand2, studentize = FALSE)

```

#### IV.III.III Error Normality Assumption

Next, we check the error normality assumption. This can be done by plotting the standardized residuals against the theoretical residuals, as shown below. Interestingly, the residuals follow normality for most of the range, except there are strong departures from normality in the tails. This model has very thick tails, particularly the right tail. This indicates that the model is a good fit for a wide range of properties; however, for a decent number of properties the model is a poor fit. 

This is likely due to the fact that the distribution of house prices has a long right tail, as most houses have a price in the range of two-hundred thousand to one million dollars, but a small subset of houses have prices spread across the wide range of one million to eight million dollars. We are probably having trouble fitting these most expensive homes, and one way to address this issue is with robust regression, which places less weight on influential outliers.  

```{r qqplot, fig.show='hold', out.width='50%'}
# Generate Q-Q plot
plot(best_ols_cand2, which = 2)

# Show distribution of home prices
ggplot(train_df) + 
  geom_density(aes(x = price)) + 
  labs(title = "Distribution of Home Prices",
       subtitle = " For the training set") + 
  theme_bw()

```

#### IV.III.IV Multicollinearity

Lastly, we check for multicollinearity in the candidate model. Variance inflation factors (VIF) are shown below for each of the predictors. Note that because the zip code term has more than one degree of freedom, the generalized VIF (GVIF) is calculated. None of the variables show signs of multicollinearity, as the VIFs are all below 5. Thus, we don't need to consider methods to remediate multicollinearity, such as Ridge and Lasso regressions. 


```{r vif_cand2}
# Check VIF
car::vif(best_ols_cand2)

```

### IV.IV Remediation

To address the issues described above, we can consider several remedial measures, including the inclusion of polynomial terms, transformation of the response variables, weighted least squares, and robust regression. 

#### IV.IV.I Variable Transformation

We can consider the possibility of a transformation of the response variable, price. To find the optimal transformation, we consider the Box-Cox method, which seeks to find the power transformation that maximizes log-likelihood. From the plot below, it appears that a transformation of 0.1 is optimal. Note that none of zero, one-half, and one are in the 95% confidence interval.

However, as raising the response to the power of 0.1 sounds strange and can be difficult to communicate to stakheholders, we will not pursue this transformation, as there may be better ways to remediate the issues with the model. 

```{r boxcox}
# Find optimal transformation
boxcox(best_ols_cand2, lambda = seq(-.2,.3,.01))
```

#### IV.IV.II Polynomial Terms

We next consider adding a second order term to the model for the continuous variables, namely square feet of living space. Note that we must center this variable first to prevent multicollinearity. The estimated model, shown below, indicates that the square term is highly significant. 

Furthermore, inclusion of the second order term provides a boost of several percentage points to the adjusted R-squared, which is now 82.6%. 

```{r poly_terms, results='asis'}
# Add square terms, but center them first
train_poly_df <- train_df %>% 
  dplyr::select(price, sqft_living, waterfront, view, grade, n_yrs_ago_built, zipcode) %>% 
  mutate(across(.cols = c(sqft_living), ~.x - mean(.x)),
         across(.cols = c(sqft_living), ~ .x^2, .names = "{.col}_2")) %>% 
  dplyr::select(price:n_yrs_ago_built, sqft_living_2, zipcode)

# Train model with poly terms
ols_poly_model <- lm(price ~ ., data = train_poly_df)

# Display results
tidy(ols_poly_model) %>% 
  dplyr::select(Term = term, Coefficient = estimate, std.error, p.value) %>% 
  mutate(Coefficient = round(Coefficient, 3),
         std.error = round(std.error, 4),
         p.value = round(p.value, 4)) %>% 
  slice(1:7) %>% 
  kable(caption = "OLS Model with Second Order Term (zip code not shown, but predictor is included in model)",
        booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")


```

##### IV.IV.II.I Polynomial Model Diagnostics

We next must test the model assumptions on the second order polynomial model, the results of which are shown below. The good news is that the plot showing residuals vs fitted values is looking much better, suggesting that the linearity assumption is somewhat more satisfied (the red line is mostly horizontal until the end, most likely due to a couple of outlying price observations). However, no progress has been made on the other two assumptions, as error variances are still very unequal and errors still have very thick tails. In fact, heteroskedasticity seems to be an even greater issue with this new model. 

```{r poly_assumptions, fig.show='hold', out.width='50%'}
# Plot all three 
par(mfrow = c(2,2))
plot(ols_poly_model, which = 1)
plot(ols_poly_model, which = 2)
plot(ols_poly_model, which = 3)
```

##### IV.IV.II.II Multicollinearity - Second Order Model

There are **no issues** with multicollinearity in the second order model. From the table below, all the VIFs are well under 5. Thus, we do not need to consider Lasso or Ridge regressions. 

```{r vif2}
# VIF
car::vif(ols_poly_model)
```


#### IV.III.I Robust Regression

To address potential outlier cases that have an large influence on the model, we can use robust regression, which puts lower weights on the influential points. This is expected to have a meaningful impact on the model's performance, since the model has been shown to struggle with fitting the more expensive properties. We use Huber weights for the robust regression. 

The results from the robust regression are shown below. All variables are significant (to conserve space, zip code is not shown, but it is included in the model). Interestingly, the AIC increased over the polynomial somewhat from 403,855 to 404,905. This is not a meaningful change in AIC, but it does suggest that the robust regression doesn't provide that much of a lift to model performance, contrary to expectations. 

Lastly, as expected the standard errors on each of the estimators decreased when compared with the initial second order model. 

```{r rlm_poly, results='asis'}
# Use Huber weights
robust_model <- rlm(price ~ ., data = train_poly_df, psi = psi.huber)

# Display results
tidy(robust_model) %>% 
  dplyr::select(Term = term, Coefficient = estimate, std.error, statistic) %>% 
  mutate(Coefficient = round(Coefficient, 3),
         std.error = round(std.error, 4)) %>% 
  slice(1:7) %>% 
  kable(caption = "Robust Regression (zip code not shown, but predictor is included in model)",
        booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")

```

#### IV.III.II Weighted Least Squares

Weighted Least Squares (WLS) may address issues with heteroskedasticity by putting less weight on observations with higher error variance. We apply WLS to the second order model by regressing absolute residuals on fitted values, and then we set the weights equal to the inverse of the square of the fitted absolute residuals. This has the effect of putting less weight on those observations that have higher error variance. 

The results are shown below. Note that adjusted R-squared drops sharply to 61.2%, whereas before it was 82.6% (in the original second order model). 

The WLS model also does not do much to address unequal variances, as shown by the plot of fitted values vs residuals and the Breusch-Pagan test. The plot continues to show a cone shape. Likewise, the p-value of the Breusch-Pagan test is nearly zero, which means we reject the null hypothesis of equal variances. 

```{r wls_model}
# Get absolute residuals and fitted values from the second order model 
resids_poly <- abs(residuals(ols_poly_model))
yhat_poly <- predict(ols_poly_model)

# Regress absolute residuals on fitted values
wts_model <- lm(resids_poly ~ yhat_poly)
wts_wls <- 1 / (predict(wts_model)^2)

# Estimate WLS model
wls_model <- lm(price ~., data = train_poly_df, weights = wts_wls)
glance(wls_model)[1:9]

plot(wls_model, which = 1)
bptest(wls_model, studentize = F)

```


### IV.V Performance Evaluation Using Test Set

Four models have been considered in this section: the linear model with six predictors, a second order model, robust regression, and weighted least squares. To compare the performance, we apply the estimated models to the test set and calculate RMSE and adjusted R-squared for each model. 

The results are shown below. OLS Candidate 1 refers to the model with only two predictors (sq ft of living space and zip code) whereas OLS Candidate 2 refers to the model with six predictors (additional variables include waterfront, view, age of home, and grade). The polynomial model is built off the second candidate OLS model. Likewise, the robust and WLS models are built off the polynomial model. 

The two best performing models are the robust and polynomial models, as they each have the lowest RMSE and highest adjusted R-squared values. Since the robust model is built off the polynomial model and provides no additional lift, we believe the polynomial model is the best model.

```{r model_comps, results='asis'}
# Prepare the test set by adding poly terms
test_poly_df <- test_df %>% 
  mutate(sqft_living = sqft_living - mean(sqft_living),
         sqft_living_2 = sqft_living^2) %>% 
  dplyr::select(price, sqft_living, sqft_living_2, waterfront, view, grade, n_yrs_ago_built, zipcode)

# Make predictions for each model using the test sample
model1_yhat <- predict(best_ols_cand1, newdata = test_df)
model2_yhat <- predict(best_ols_cand2, newdata = test_df)
model2poly_yhat <- predict(ols_poly_model, newdata = test_poly_df)
rlm_yhat <- predict(robust_model, newdata = test_poly_df)
wls_yhat <- predict(wls_model, newdata = test_poly_df)

# Calculate RMSE for each model
y_actual <- test_poly_df %>% pull(price)
n_test <- nrow(test_poly_df)
rmse_ols1 <- sqrt(sum((y_actual - model1_yhat)^2) / n_test)
rmse_ols2 <- sqrt(sum((y_actual - model2_yhat)^2) / n_test)
rmse_poly <- sqrt(sum((y_actual - model2poly_yhat)^2) / n_test)
rmse_rlm <- sqrt(sum((y_actual - rlm_yhat)^2) / n_test)
rmse_wls <- sqrt(sum((y_actual - wls_yhat)^2) / n_test)

# SST and SSE
sst_test <- sum((y_actual - mean(y_actual))^2)
sse_cand1_test <- sum((y_actual - model1_yhat)^2)
sse_cand2_test <- sum((y_actual - model2_yhat)^2)
sse_poly_test <- sum((y_actual - model2poly_yhat)^2)
sse_rlm_test <- sum((y_actual - rlm_yhat)^2)
sse_wls_test <- sum((y_actual - wls_yhat)^2)

# Calculate adjusted R-squared for each model
n <- nrow(test_df)
adj_rsq_cand1 <- calc_rsq_adj(n, best_ols_cand1$rank - 1, sse_cand1_test, sst_test)
adj_rsq_cand2 <- calc_rsq_adj(n, best_ols_cand2$rank - 1, sse_cand2_test, sst_test)
adj_rsq_poly <- calc_rsq_adj(n, ols_poly_model$rank - 1, sse_poly_test, sst_test)
adj_rsq_rlm <- calc_rsq_adj(n, ols_poly_model$rank - 1, sse_rlm_test, sst_test)
adj_rsq_wls <- calc_rsq_adj(n, ols_poly_model$rank - 1, sse_wls_test, sst_test)


rmse_df <- tibble(Model = c('OLS Candidate 1', 'OLS Candidate 2', 'Polynomial', 'Robust', 'WLS'), 
                  RMSE = c(rmse_ols1, rmse_ols2, rmse_poly, rmse_rlm, rmse_wls),
                  `Adj. R-Squared` = c(adj_rsq_cand1, adj_rsq_cand2, adj_rsq_poly, 
                                      adj_rsq_rlm, adj_rsq_wls))

kable(rmse_df, 
      format.args = list(big.mark = ","),
      caption = ' Root Mean Squared Error (RMSE) and Adjusted R-squared on the Test Set',
      booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")

```

Thus, the final model contains the following predictors:

**Price = sqft_living + sqft_living_2 + waterfront + view + grade + n_yrs_ago_built + zipcode**


\newpage
## V. Challenger Models (15 points)

```{r section v data preparation}
# Train and Test Data already prepared during OLS phase, just copying dataframes
train_data <- train_df
test_data <- test_df
```

### V.I Regression Tree

```{r creating regression tree}
# Create Regression Tree Based on Predictors in Section III

library(rpart)
reg_tree <- rpart(price ~ ., data = train_data, cp=0.001)
reg_tree
```

```{r tree plot, fig.width=10, fig.height=10}
# plot tree
library(rpart.plot)
rpart.plot(reg_tree, digits = 3)
```

### V.II Regression Tree Performance Evaluation

```{r eval2}
# IN SAMPLE TEST (Train Data)

price_predict <- predict(reg_tree, train_data)
summary(price_predict) #summary of predicted values

summary(train_data$price) #summary of actual values

corr_insample <- cor(price_predict, train_data$price)

# Measuring performance with the mean absolute error
MAE <- function(actual, predicted) {mean(abs(actual - predicted))}
mae_in_sample <- MAE(train_data$price, price_predict)

# Calculate RMSE
rmse_reg_tree_in_sample <- sqrt(sum((train_data$price - price_predict)^2) / nrow(train_data))

# Measuring performance with the SSE
SSE <- function(actual, predicted) {sum((actual - predicted)^2)}
sse_in_sample <- SSE(train_data$price, price_predict)

# Measuring performance with the R-square
R2 <- function(actual, predicted) {sum((actual - predicted)^2)/((length(actual)-1)*var(actual))}
r2_tree_train <- 1 - R2(train_data$price, price_predict)

```

```{r eval1}
# OUT OF SAMPLE TEST (Test Data)

price_predict <- predict(reg_tree, test_data)
summary(price_predict) #summary of predicted values

summary(test_data$price) #summary of actual values

cor_test <- cor(price_predict, test_data$price)

# Measuring performance with the mean absolute error
MAE <- function(actual, predicted) {mean(abs(actual - predicted))}
mae_test <- MAE(test_data$price, price_predict)

# Calculate RMSE
rmse_reg_tree_test <- sqrt(sum((test_data$price - price_predict)^2) / nrow(test_data))


# Measuring performance with the SSE
SSE <- function(actual, predicted) {sum((actual - predicted)^2)}
reg_sse_test <- SSE(test_data$price, price_predict)

# Measuring performance with the R-square
R2 <- function(actual, predicted) {sum((actual - predicted)^2)/((length(actual)-1)*var(actual))}
r2_tree_test <- 1 - R2(test_data$price, price_predict)


# Present Results
rmse_df_in_out_sample <- tibble(Test = c('In Sample (Train)', 'Out of Sample (Test)'),
                  `Correlation` = c(corr_insample, cor_test),
                  MAE = c(mae_in_sample, mae_test),
                  SSE = c(sse_in_sample, reg_sse_test),
                  RMSE = c(rmse_reg_tree_in_sample, rmse_reg_tree_test),
                  "$R^2$" = c(r2_tree_train, r2_tree_test))

kable(rmse_df_in_out_sample, 
      format.args = list(big.mark = ","),
      caption = 'In-Sample versus Out-of-Sample comparison',
      booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")
```


## V.II Conclusion

Based on the results for both the out-of-sample and in-sample tests for the model, we believe this regression tree model is fit for purpose as its results are similar to the results obtained from the regression models in earlier sections. When compared to the polynomial model developed in *Section IV.IV.II*, the regression tree model developed in this section performs slightly worse when comparing its out-of-sample results. However, when looking at its in-sample results, the regression tree performed better than the polynomial model in both its R-squared and RMSE metrics.


\newpage
## VI. Model Limitation and Assumptions (15 points)

Based on the test sample results for all of our models, we choose the Polynomial model as our champion model. Its prediction performance is the best out of all models tested, with both the lowest SSE +  RMSE values and highest Adjusted R-Squared. Looking at the Q-Q plot of the residuals we can see that once again the polynomial model shows the best distribution of residuals [Appendix A]. 

```{r model comparison}
# Getting the SSE of our models
rmse_df <- tibble(
  Model = c('OLS Candidate 1', 'OLS Candidate 2', 'Polynomial', 'Robust', 'WLS', 'Regression Tree'),
  `SSE` = c(sse_cand1_test, sse_cand2_test, sse_poly_test, sse_rlm_test, sse_wls_test, reg_sse_test),
  RMSE = c(rmse_ols1, rmse_ols2, rmse_poly, rmse_rlm, rmse_wls, rmse_reg_tree_test),
  `Adj. R-Squared` = c(adj_rsq_cand1, adj_rsq_cand2, adj_rsq_poly, adj_rsq_rlm, adj_rsq_wls, r2_tree_test))

kable(rmse_df, 
      format.args = list(big.mark = ","),
      caption = 'Sum Squared of Errors, Root Mean Squared Error (RMSE) and 
      Adjusted R-squared on the Test Set',
      booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")
```

## VI.I Assumptions
There are several assumptions that must be made in order to support the champion model. Foremost is that the data is not perfectly clean, with the existence of several large outliers which have larger than normal leverage over the whole model. We found that, while this was somewhat problematic, the benefits of adjusting the model to better explain the outliers ultimately did more harm than good. Likewise, we follow the rationale that most prices will tend to mean/median of the county. This is due to factors external to that which is measured by the dataset, such as fair market competition. As such, going forward we would expect there to be few additional outliers.

Likewise, one must assume that the heteroskedasticity of the models is at acceptable levels. VIF tests of our models show that multicollinearity is as acceptable levels. Even with BoxCox transformations, while the graphs may appear to look normal and heteroskedasticity solved, follow up Breusch-Pagan tests reveal that we still cannot reject the null hypothesis [Appendix B]. As a result we have decided that other remedial measures would be more acceptable and better explained to potential stakeholders. 

## VI.II Limitations
There are several limitations to the models presented here.

The first limitation is the time period over which the data has been collected. Given that the data only encompasses roughly 1 year of data collection, certain macro-economic effects can not be measured despite their real world influence. Aspects such as seasonality and year-over-year trends can not be extracted with the current data. Another source of influence that can not be measured within this dataset is the impact of market interest rates which, as recent years have shown, hold large influence on the price of housing and rent. We additionally have the limitation of this data being collected from a single county within the United States. The relatively small geographic concentration of this data consequently means that the use of the models outside of the local area would be meaningless.


\newpage
## VII. Ongoing Model Monitoring Plan (5 points)

There are several aspects which must be considered when monitoring ongoing performance of the existing model. 

To start we must first address data inconsistencies and missing context information. In our initial data exploration phase we identified several variables that lacked clarity, such as the bathrooms, sqft_lot, and grade. For the bathrooms variable, it exists as a sum of several constituent components. It is recommended for future data collection to identify the individual components of the bathroom, as described in Section II, and tally that count for more precise data interpretation (For example, interpretation of 3.75). For sqft_lot, we identified some inconsistencies within the measurements that would have been better explained with more robust data clarification. As for the grade variable, this is a largely subjective entity. It exists as a matter of personal or arbitrary judgments on the part of the individual(s) assessing the property. No information is given as to the criterion used in determining the grade, nor is there any note of if those criteria were ever changed throughout the data collection process. 

Therefore it is our overall recommendation, that in the ongoing monitoring of the model, to note any changes in the approach to data collection. More precise data collection would have substantial ramifications on the quality of the existing model. One such example would be if the factors determining the grade of homes were to change and all houses reassessed. This could potentially lead to changes in the predictive qualities of the variable and would force us to reconsider our models.  

Next, in the OLS models, we note that the variables which have the largest influence over sale price mostly consist of factors external to the house itself. That is, factors which either require substantial development of the home or are inherent to the location of the house. Considering first the square feet of living space and the grade of the home, these are factors that, while they can be changed, are also subject to regulatory policies. To accurately maintain future performance of this model, our next suggestion is to closely monitor regulations involving housing developments and renovations. New legislation could change new housing developments or mandate that certain changes be made to existing ones. Any such changes would have to be noted and consequently measured over time to determine whether or not they had any influential impact on the model. Should changes to the model be observed, perhaps additional variables should then be considered for model performance.

Quantitative thresholds that should be considered are primarily centered around the existence of outliers and the RMSE, Root Mean Square Error, of the model. The best performance metric we were able to achieve with our models is $RMSE = 163,999.0$ with $Adj. R^2 = 0.8110829$ for polynomial regression and $RMSE = 176,995.5$ with $Adj. R^2 = 0.7824997$ for the regression tree. These out-of-sample test results should be used as benchmarks going forward, with future models attempting to either reduce RMSE or increase adjusted R-squared, preferably both. For data outliers, as can be seen in figure ###, the presence of said outliers presents a challenge in correctly fitting the model to the data. Should further data compound these issues then additional remedial measures must be taken to properly adjust the model for best fitment.

We can also look to existing recommendations given by the Federal Reserve in regards to model risk management. Per the supervisory guidance, we must first admit that "[our] model may have fundamental errors and may produce inaccurate outputs when viewed against the design objective and intended business uses"[2]. We believe this to be true given the nature of errors we identified in the model, such as high multicollinearity between several variables, heteroskedasticity issues, and some slight departures from normality. However we assume that despite these issues, the performance of the model remains robust and is viable for sale price prediction. 

Likewise the National Association of Insurance Commissioners, a regulatory board overseeing matters of public and private insurance, recommends that model performance be assessed in combination with real world feedback from businesses and users of the model [3]. In their white paper, they discuss that only individuals with sufficient skills, knowledge and domain expertise should be responsible for the successful assessment of any particular model. This is due to complex statistical nature inherent to these models which some may find difficult to both understand and explain to other stakeholders their significance.

Finally, it should be noted that a "challenge from model users may be weak if the model does not materially affect their results"[2]. This is to say that if the model is taken with blind faith, there may be adverse business effects further down the line. This is why we present here several challenger models for price prediction, utilizing both traditional statistical methods of creating OLS models, as well as regression tree models. The ability to compare the performance of these models is crucial in understanding their individual strengths and weaknesses. Going forward  we expect that the same approach should be had in order to maintain consistent and relevant model performance.


\newpage
## VIII. Conclusion (5 points)

```{r section viii conclusion}
rmse_df <- tibble(Model = c('Polynomial', 'Reg. Tree'),
                  RMSE = c(rmse_poly, rmse_reg_tree_test),
                  `Adj. R-Squared` = c(adj_rsq_poly,  r2_tree_test))

kable(rmse_df,
      format.args = list(big.mark = ","),
      caption = ' Root Mean Squared Error (RMSE) and Adjusted R-squared on the Test Set',
      booktabs = T) %>%
  kable_styling(full_width = F,
                latex_options = "HOLD_position")
```

### VIII.I Champion Model
The results of the Regression Model in **Section V** showed that the Polynomial Model performed developed in **Section IV.IV.II** better than all the alternative models developed during the process, with the robust model having similar results but slightly worse. As shown in the table above, the polynomial model has an R-squared of 0.8110829 and an RMSE of 163,999.

### VIII.II Challenger Model
As for our challenger model from section V, the **Regression Tree** did not performed poorly, but had slightly worse results than the polynomial model. As shown in the table above, the R-squared of the regression tree is 0.7824997, and its RMSE is 176,995.5.

### VIII.III - Winner: Champion Model
Based on these results, the Polynomial Model from section III is the most ideal model for our data, as it provides the highest R-squared value and the lowest RMSE. In addition, when taking into account the assumptions and limitations mentioned in section VI, the polynomial model's performance is very high. However, if all those assumptions and limitations were to be addressed, the performance of both the polynomial model and the regression tree could either increase or decrease, and the regression tree could become the most ideal model since the current results are not too far away from each other. But as things stand right now, the polynomial model is the most ideal model based on the data available, our assumptions, and the limitations. 

\newpage

## Bibliography (7 points)

*Please include all references, articles and papers in this section.*

[1] Wikipedia. *King County, Washington.* [https://en.wikipedia.org/wiki/King_County,_Washington](https://en.wikipedia.org/wiki/King_County,_Washington).

[2] Board of Governors of the Federal Reserve System. *SR Letter 11-7: Supervisory Guidance on Model Risk Management.* 2011.  [https://www.federalreserve.gov/supervisionreg/srletters/sr1107a1.pdf](https://www.federalreserve.gov/supervisionreg/srletters/sr1107a1.pdf).

[3]  National Association of Insurance Commissioners. *Casualty Actuarial and Statistical (C) Task Force Regulatory Review of Predictive Models White Paper*. August 27, 2020. [https://portal.ct.gov/cid/-/media/CID/Regulatory-Review-of-Predictive-Models-White-Paper.pdf](https://portal.ct.gov/cid/-/media/CID/Regulatory-Review-of-Predictive-Models-White-Paper.pdf)

[4] Yuko, Elizabeth. *The Actual Difference Between a Half, 3/4, and Full Bathroom*. April 10, 2012. [https://lifehacker.com/the-actual-difference-between-a-half-3-4-and-full-bat-1848773483](https://lifehacker.com/the-actual-difference-between-a-half-3-4-and-full-bat-1848773483).

[5] Pacheco, Kaitlyn. *The 2022 U.S. Lot Size Index*. August 5, 2022. [https://www.angi.com/articles/lot-size-index.htm](https://www.angi.com/articles/lot-size-index.htm).

[6] Kutner, Nachtsheim, Neter, Li. *Applied Linear Statistical Models, Fifth Edition*. 2005.

\newpage

## Appendix (3 points)

### A. OLS Q-Q Plots

```{r Q-Q plots}
# Move to Appendix A
par(mfrow=c(2,3))
plot(best_ols_cand1, which=2, main = "Figure A-1. OLS Candidate 1 Q-Q Plot")
plot(best_ols_cand2, which=2, main = "Figure A-2. OLS Candidate 2 Q-Q Plot")
plot(ols_poly_model, which=2, main = "Figure A-3. Polynomial Regression Q-Q Plot")
plot(robust_model, which=2, main = "Figure A-4. Robust Regression Q-Q Plot")
plot(wls_model, which=2, main = "Figure A-5. WLS Regression Q-Q Plot")
```

\newpage

### B. Breush-Pagan Tests of OLS Models

Here we explore the results of Breusch-Pagan Tests as they relate to our OLS Models. We provide a Box-Cox transformation of our champion model to show that any such transformation does not provide meaningful changes to the quality of the model.
```{r bp}
# Move to Appendix B
bptest(best_ols_cand1, studentize = FALSE)
bptest(best_ols_cand2, studentize = FALSE)
bptest(ols_poly_model, studentize = FALSE)
bptest(robust_model, studentize = FALSE)
bptest(wls_model, studentize = FALSE)

boxcox(ols_poly_model, lambda = seq(-.2,.3,.01))
log_poly <- lm(log(price) ~ ., data = train_poly_df)
plot(log_poly, which=3, main = "Figure B-1. Log-Polynomial Scale-Location Plot")
plot(ols_poly_model, which=3, main = "Figure B-2. Polynomial Regression Scale-Location Plot")

tidy(log_poly) %>% 
  dplyr::select(Term = term, Coefficient = estimate, std.error, p.value) %>% 
  mutate(Coefficient = round(Coefficient, 3),
         std.error = round(std.error, 4),
         p.value = round(p.value, 4)) %>% 
  slice(1:7) %>% 
  kable(caption = "OLS Model with Second Order Term and Log Transformed Price",
        booktabs = T) %>% 
  kable_styling(full_width = F,
                latex_options = "HOLD_position")

bptest(log_poly, studentize=FALSE)
```

\newpage

### C. Exploratory Analysis of Additional Variables
The following sections include additional plots of variables that  were not included in the final models.

#### Bedrooms

```{r bedrooms scatter plots, box plots, histograms}
# bedrooms box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$bedrooms, main = "Figure C-1. bedrooms Box Plot")
hist(kc_house_sales$bedrooms, main = "Figure C-2. bedrooms  Distribution")
par(mfrow=c(1,2))
plot(kc_house_sales$bedrooms, kc_house_sales$price,  main = "Figure C-3. bedrooms Scatter Plot");
abline(lm(price ~ bedrooms, data = kc_house_sales), col = "red")
```
  
Looking at the number of bedrooms and the box plot in Figure C-1, there are outliers on the lower and upper ends of the range of bedroom values, with one observation having more than 30 bedrooms. Per Figure C-2, it appears as though the vast majority of houses have between two and four bedrooms. It would be interesting to know the state of the "houses" with 0 bedrooms--are these studio apartments, cabins, plots of bare land, houses that have been gutted or otherwise have no interiors and thus no bedrooms, commercial properties accidentally included in the data set, typos, or is there another explanation?  

Figure C-3 displays what appears to be a curvilinear relationship between the number of bedrooms and the house price, increasing until reaching five bedrooms and then falling again. 

\newpage

#### Bathrooms

```{r bathrooms scatter plots, box plots, histograms}
# bathrooms box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$bathrooms, main = "Figure C-4. bathrooms Box Plot")
hist(kc_house_sales$bathrooms, main = "Figure C-5. bathrooms Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$bathrooms, kc_house_sales$price,  main = "Figure C-6. bathrooms Scatter Plot");
abline(lm(price ~ bathrooms, data = kc_house_sales), col = "red")
```
  
The bathroom predictor variable presented confusion upon first glance. Assuming the data is for residential real estate in the King County district, it seems odd that it would be possible for a house to have less than one full bathroom, yet there were multiple observations with less than 1.0 bathroom (and some with 0 bathrooms or fractions of a bathroom ending in .25). Upon researching the definitions used for bathroom terminology in the real estate industry [4], it appears as though each major component of a bathroom--toilet, sink, shower, and tub--counts as 0.25. It might have been more interesting for the bathroom data to be split into two columns: full_bathrooms and partial_bathrooms since, for example, if a house has 2 bathrooms according to the data set, it is unclear whether that means two full bathrooms, one full bathroom and two half bathrooms (toilet and sink), or another configuration. As for the houses with less than 1.0 bathroom, it would be interesting to know the reason--is the house unfinished? Is it a tiny house with just a composting toilet in the bathroom?

Overall, per Figure C-4 and Figure C-5, most houses have around 2 bathrooms, with outliers at the lower and upper end of the ranges. Per Figure C-6, it appears as though there is a linear relationship between number of bathrooms and price of the house.

\newpage

#### Square Footage - Lot

```{r housing square footage lot scatter plots, box plots, histograms}
# sqft_lot box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$sqft_lot, main = "Figure C-7. sqft_lot Box Plot")
hist(kc_house_sales$sqft_lot, main = "Figure C-8. sqft_lot Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$sqft_lot, kc_house_sales$price,  main = "Figure C-9. sqft_lot Scatter Plot");
abline(lm(price ~ sqft_lot, data = kc_house_sales), col = "red")
```

Per Figure C-7 and Figure C-8 showing the box plot and distribution of the sqft_lot it appears as though the lot size is very concentrated around the lower end of the spectrum, with a few extreme outliers. According to the scatter plot in C-9, it looks like there is somewhat of a negative linear relationship between lot size and house price.

Looking at some of the individual data points, it seems as though some of the lot sizes might be impossible considering the square footage of the living area.  For example, the row with ID 9828702895 has a sqft_lot size of 520, a sqft_living of 2420, no basement (sqft_above is also 2420), and only 1.5 floors. With only 1.5 floors and no basement, it does not seem possible to have a square footage of 2420 sqft on a lot size of 520 sqft, considering that the lot size typically includes the house's footprint [5]. Unfortunately, without further clarification, it is not possible to exclude data points based on this rationale. The "square footage of the land space" definition provided with the data set could mean the land excluding the house's footprint.

\newpage

#### Square Footage - Above Ground

```{r housing square footage above scatter plots, box plots, histograms}
# sqft_above box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$sqft_above, main = "Figure C-10. sqft_above Box Plot")
hist(kc_house_sales$sqft_above, main = "Figure C-11. sqft_above Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$sqft_above, kc_house_sales$price,  main = "Figure C-12. sqft_above Scatter Plot");
abline(lm(price ~ sqft_above, data = kc_house_sales), col = "red")
```

Per Figure C-10 and C-11, the median square footage above ground appears to be slightly less than 2000 sqft, with outliers present at the higher end of the range.

Per Figure C-12, there appears to be a linear relationship between square feet of living space and price, with price increasing as the square footage increases.  

\newpage

#### Floors

```{r floors scatter plots, box plots, histograms}
# floors box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$floors, main = "Figure C-13. floors Box Plot")
hist(kc_house_sales$floors, main = "Figure C-14. floors Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$floors, kc_house_sales$price,  main = "Figure C-15. floors Scatter Plot");
abline(lm(price ~ floors, data = kc_house_sales), col = "red")
```
  
Per Figures C-13, the median house has 1.5 floors, and there are no outliers in the data set. Although the median is 1.5 floors, looking at the distribution in Figure C-14, most houses have either 1 floor or 2 floors.

Looking at Figure C-15, there appears to be a nonlinear relationship between nnumber of floors and price. Houses with 1 floor or 2 floors appear to have a wider price range with higher maximum prices than houses with a fractional floor or those with 3 foors.

\newpage

#### Condition

```{r condition scatter plots, box plots, histograms}
# condition box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$condition, main = "Figure C-16. condition Box Plot")
hist(kc_house_sales$condition, main = "Figure C-17. condition Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$condition, kc_house_sales$price,  main = "Figure C-18. condition Scatter Plot");
abline(lm(price ~ condition, data = kc_house_sales), col = "red")
```
  
The box plot in Figure C-16 indicates that the median house has a condition of 3, which is average, and houses with a condition of 1 are outliers. Figure C-17 with the distribution again shows that the vast majority of houses have a condition of 3. Interestingly, in the scatter plot in Figure C-18, it appears as though if the condition is at least 3, there is not much of an impact on housing price, but below 3 and the price decreases.

\newpage

#### Neighbor Square Footage - Lot

```{r neighbor square footage lot scatter plots, box plots, histograms}
# sqft_lot15 box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$sqft_lot15, main = "Figure C-19. sqft_lot15 Box Plot")
hist(kc_house_sales$sqft_lot15, main = "Figure C-20. sqft_lot15 Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$sqft_lot15, kc_house_sales$price,  main = "Figure C-21. sqft_lot15 Scatter Plot");
abline(lm(price ~ sqft_lot15, data = kc_house_sales), col = "red")
```
  
According to the box plot and histogram in Figure C-19 and C-20, the lot size of the 15 closest neighbors is generally grouped around 0, with outliers at the higher end of the range. It would be interesting to learn whether the outliers are indeed the correct lot sizes or whether there are typos or other errors in the data set. The scatter plot in Figure C-21 appears to show somewhat of a negative linear relationship between price and the square footage of lot size of the nearest 15 neighbors. Since King County encompasses Seattle, it is likely that most houses near the city do not have that much land surrounding them. Perhaps houses closer to the city center, which likely have smaller lot sizes, are worth more.

\newpage

#### Neighbor Square Footage - Living

```{r neighbor square footage living scatter plots, box plots, histograms}
# sqft_living15 box plot, histogram, scatter plot vs. price
par(mfrow=c(1,2))
boxplot(kc_house_sales$sqft_living15, main = "Figure C-22. sqft_living15 Box Plot")
hist(kc_house_sales$sqft_living15, main = "Figure C-23. sqft_living15 Distribution")
par(mfrow=c(1,1))
plot(kc_house_sales$sqft_living15, kc_house_sales$price,  main = "Figure C-24. sqft_living15 Scatter Plot");
abline(lm(price ~ sqft_living15, data = kc_house_sales), col = "red")
```
According to the box plot and histogram in Figure C-22 and C-23, the square footage of living space among the 15 closest neighbors is grouped around slightly under 2000 square feet, with outliers at the higher end of the range. The scatter plot in Figure C-24 shows a linear relationship between the square footage of living space of the 15 nearest neighbors and price. 