---
title: "Final Project Scratch Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r}
## Helper to display regression function with n coefficients
dispRegFunc <- function(reg) {
  coefs <- reg$coefficients
  b0 = coefs[1]
  n <- length(coefs)
  my_formula <- paste0("Y = ", round(b0, digits = 6))
  for (i in 2:n) {
    my_formula <- paste0(my_formula, " + ", round(coefs[i],6), names(coefs)[i])
  }
  my_formula
}
```

Step 0: joined team

Step 1: Load Data and review variables
```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Import libraries
library(readr)
library(ggplot2)
library(corrplot)
library(MASS)
library(datasets)
library(olsrr)
library(car)
theme_set(theme_bw())

# Import data and adjust settings
HouseSales<-read.csv("KC_House_Sales.csv")
set.seed (1023)
options("scipen" = 10)

# Check for NA's
str(HouseSales)
#check for missing and NAs
apply(HouseSales,2,function(x) sum(is.na(x)))

# Cleaning the Price column
summary(HouseSales)
head(HouseSales$price)

HouseSales$price<-gsub(" ","",as.character(HouseSales$price))
HouseSales$price[1]

HouseSales$price<-gsub("\\$","",as.character(HouseSales$price))
HouseSales$price[1]

HouseSales$price<-gsub(",","",as.character(HouseSales$price))
HouseSales$price[1]


HouseSales$price <- as.numeric(HouseSales$price)
summary(HouseSales)

# Cleaning the date column
head(HouseSales$date)

HouseSales$date <-gsub("T.*","",HouseSales$date)
HouseSales$date[1]

year <- substr(HouseSales$date, 0, 4)
month <- substr(HouseSales$date, 5, 6)
day <- substr(HouseSales$date, 7, 8)
```


Step 2: Divide Data into train and test sets, 70/30 split
```{r divide data, include=FALSE}
n <- dim(HouseSales)[1]
ind = sample(c(1:n), n*0.7)
H.train <- HouseSales[ind,]
H.test <- HouseSales[-ind,]
```


Step 3: Inspect Data and Drop variables, create categorical variables
```{r Dropping variables}
#summary(H.train)

# Dropping unneeded variables
drop <- c("id","lat","long", "date", "zipcode", "sqft_basement")
df = H.train[,!(names(H.train) %in% drop)]
df.test = H.test[,!(names(H.test) %in% drop)]
summary(df)
attach(df)
```

```{r plot inspection}
# boxplots for starting reference
par(mfrow=c(2,2))
g1 <- ggplot(H.train, aes(sqft_living))
g1 + geom_boxplot(varwidth=T, fill="plum") + 
    labs(title="Box plot", 
         subtitle="Total Interior Square Footage",
         caption="Source: HouseSales",
         x="Square Feet of Interior Living Space")

g2 <- ggplot(H.train, aes(sqft_lot))
g2 + geom_boxplot(varwidth=T, fill="orange") + 
    labs(title="Box plot", 
         subtitle="Total Lot (Exterior) Square Footage",
         caption="Source: HouseSales",
         x="Square Feet of Lot Space")

g3 <- ggplot(H.train, aes(sqft_above))
g3 + geom_boxplot(varwidth=T, fill="green") + 
    labs(title="Box plot", 
         subtitle="Total Interior Square Footage Above Ground Level",
         caption="Source: HouseSales",
         x="Square Feet of Interior Living Space Above Ground Level")

g4 <- ggplot(H.train, aes(sqft_basement))
g4 + geom_boxplot(varwidth=T, fill="cyan") + 
    labs(title="Box plot", 
         subtitle="Total Interior Basement Square Footage",
         caption="Source: HouseSales",
         x="Square Feet of Interior Living Space Below Ground Level")

g5 <- ggplot(H.train, aes(price))
g5 + geom_boxplot(varwidth=T, fill="chocolate") + 
    labs(title="Box plot", 
         subtitle="Price",
         caption="Source: HouseSales",
         x="Price")

g5 <- ggplot(H.train, aes(sqft_living15))
g5 + geom_boxplot(varwidth=T, fill="coral") + 
    labs(title="Box plot", 
         subtitle="Total Interior Basement Square Footage",
         caption="Source: HouseSales",
         x="Square Feet of Interior Living Space Below Ground Level")

g6 <- ggplot(H.train, aes(sqft_lot15))
g6 + geom_boxplot(varwidth=T, fill="azure2") + 
    labs(title="Box plot", 
         subtitle="Total Interior Basement Square Footage",
         caption="Source: HouseSales",
         x="Square Feet of Interior Living Space Below Ground Level")

```

Step 4: Build regression model to predict price
```{r model}
summary(df)
class(df)
#H.full <- lm(price ~ ., data=df)
H.full <- lm(price ~ bedrooms + bathrooms + sqft_living + sqft_lot + floors + waterfront + view + condition + grade + sqft_above + yr_built + yr_renovated + sqft_living15 + sqft_lot15)
summary(H.full)
plot(H.full)
```

Step 5: Creating scatter plots and correlation matrix for the train data + result interpretation

**Interpretation:**

|       Scatter Plots: 
|
|       Correlation Matrix: The matrix shows some issues of multi-collinearity are appearing with several of the variables. We can see that sqft_living is strongly correlated with sqft_above (0.87). This makes sense as these two values are closely related with each other. Usually much of the livable space of a house is also located above ground level, hence the relationship. Additional string correlations are seen between sqft_above & grade(0.76), sqft_above & sqft_above15(0.76), sqft_living & price(0.7), as well as several others. As a result of these correlations, we will have to address issues of multi-collinearity within our model.
|
|       VIF helps determine the severity of multicollinearity. Previous concerns with sqft_living and sqft_above seem to hold some weight as these two predictors have the heighest VIFs, though still below our decision point of $VIF < 10$.

```{r Scatter plots}
# Scatter plots needed: Leverages vs. Index,  Residuals vs Leverage, hat matrix, Studentized Residuals vs. Leverage, 
n <- nrow(df)
p <- length(H.full$coefficients)
hii<- hatvalues(H.full)


# Hat Matrix
plot(sqft_living~bathrooms, pch=16 )
text(bathrooms +0.5, sqft_living,
labels=as.character(1:length(bathrooms)),col="red")
index<-hii>2*p/n
points( bathrooms[index], sqft_living[index], cex=2.0, col="blue")
```


```{r Scatter plots2}
# Residuals vs. Leverage
plot(H.full, which=5, main='Average total score on the SAT, 1994-95')

# Leverages vs. Index

plot(hii, ylab="Leverages",main="Leverages vs Index Plot")
abline(h=2*p/n,col="red")

####Studentized Residuals vs Leverage Plot ####
#Graph for detecting influential observations.

ols_plot_resid_lev(H.full)
```


```{r Scatter plots4}
# Scatter plots
ggplot(df, aes(sqft_living15, price)) +
   geom_point() +
   ggtitle("Scatter Plot")
ggplot(df, aes(sqft_lot, price)) +
   geom_point() +
   ggtitle("Scatter Plot")
ggplot(df, aes(sqft_above, price)) +
   geom_point() +
   ggtitle("Scatter Plot")
ggplot(df, aes(floors, price)) +
   geom_point() +
   ggtitle("Scatter Plot")

ggplot(df, aes(H.full$fitted.values, H.full$residuals)) +
   geom_point() +
   ggtitle("Scatter Plot")
```


```{r Scatter plots5}
# Correlation Matrix
cor_matrix <- round(cor(df),3)

cor_matrix

corrplot(cor_matrix, method="number", addCoef.col = 1,number.cex = 0.5, tl.cex = 0.7)
```


```{r Scatter plots6}
# Supporting VIF for multicollinearity
vif(H.full)
```

```{r}
boxcox(H.full,seq(-1,1,0.1))
```




Step 6: Build the best multiple linear models by using the stepwise selection method. Compare the performance of the best two linear models.

|       First model is made using the best subset selection method

```{r stepwise selection}
# Step 1: Variable validation using: best_subset, 

# BE CAREFUL WHEN RUNNING THIS BLOCK AS IT IS COMPUTE INTENSIVE
k1<-ols_step_best_subset(H.full)
k1
plot(k1,guide="none")
summary(k1)
```


```{r stepwise selection2}
k2 <- ols_step_backward_p(H.full, prem = 0.05)
k2
plot(k2)
```
```{r}
library(leaps)
k3 <- regsubsets(price~., data=df)
rs<-summary(k3)

# Plotting the adjusted R-square values against number of parameters
plot(2:9, rs$adjr2, xlab="Number of Parameters", ylab="Adjusted R-square")
which.max(rs$adjr2)

# Plotting the CP values against number of parameters
plot(2:9, rs$cp, xlab="Number of Parameters", ylab="Cp Statistic")
abline(0,1)

rs$which
k4 <- lm(price ~ sqft_living + grade + yr_built + waterfront + view + bedrooms + bathrooms + sqft_lot15, data=df)
ols_mallows_cp(k4, H.full)
summary(k4)
par(mfrow=c(2,2))
plot(k4)
dispRegFunc(k4)
```




```{r stepwise selection3, include=FALSE, echo=FALSE}



# Ignore thise code, this is all extra carry over 
#
#
#
#
#


#k2 <- ols_step_backward_p(H.full,prem = 0.05,details=FALSE)
#k2
# Step 1: Centering the variables due to high levels of correlation between the variables, will be testing interaction terms
#wealth <- fort.dat$wealth
#age <- scale(fort.dat$age, scale=FALSE)
#rA <- fort.dat$region_A
#rE <- fort.dat$region_E
#rM <- fort.dat$region_M
#rO <- fort.dat$region_O
#rU <- fort.dat$region_U

# Step 2: Backwards stepwise
#fort.full <- lm(wealth ~ age + rA + rE + rM + rO + rU + age:rA + age:rE + age:rM + age:rO + age:rU)
#summary(fort.full)
#back.m <- ols_step_backward_p(fort.full)
#back.m
#fort.back <- lm(wealth ~ rA + rE + rM + rO  + age:rM + age:rU)
#summary(fort.back)
#par(mfrow=c(2,2))
#plot(fort.back)

# Step 3: Forwards stepwise
#step.m <-ols_step_forward_p(fort.full, penter = 0.05)
#step.m
#fort.step <- lm(wealth ~ rM)
#summary(fort.step)
#par(mfrow=c(2,2))
#plot(fort.step)
```

